\documentclass[t]{beamer}
\usepackage{multicol}

\usetheme{default}
\setbeamertemplate{navigation symbols}{}

%\mode<presentation>
%{
%  \usetheme{Warsaw}
%  % or ...
%
%  \setbeamercovered{transparent}
%  % or whatever (possibly just delete it)
%}


\usepackage[english]{babel}
% or whatever

\usepackage[latin1]{inputenc}
% or whatever

\usepackage{times}
\usepackage[T1]{fontenc}
% Or whatever. Note that the encoding and the font should match. If T1
% does not look nice, try deleting the line with the fontenc.


%\usepackage{verbatim}
\usepackage{colortbl}

 %\newrgbcolor{hilight}{0.000 1.000 0.000}   % green
 %\xdefinecolor{hilight}{rgb}{0.000 1.000 0.000} % green
 %\newcommand{\hilight}{\color{blue}}
 %\xdefinecolor{MyGreen}{rgb}{0.000, 0.500, 0.000} % green
 \colorlet{myred}{red!90!black} % slightly darker than normal red
 \colorlet{myblue}{cyan}        % plain cyan works; might consdier darkening
 \colorlet{mygreen}{green!70!black} % slightly darker than normal green
 %\newcommand{\nonliteral}{\color{MyGreen}}

 \newenvironment{myitemize}
                {
                  \begin{itemize}
                    \setlength{\itemsep}{0pt}
                    \setlength{\parskip}{-0.125\baselineskip}
                    \setlength{\parsep} {0pt}
                }%
                {\end{itemize}}

\title{Merging in Git}

\author{Elijah Newren}
\institute{}

\date{}

\subject{Talks}
% This is only inserted into the PDF information catalog. Can be left
% out.



% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}



% If you wish to uncover everything in a step-wise fashion, uncomment
% the following command:

%\beamerdefaultoverlayspecification{<+->}


\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Overview}
  \tableofcontents
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Three-way content merge}

\begin{frame}
  \frametitle{Three-way content merge}

  \begin{multicols}{2}
    File from branch A:\\
    {\footnotesize\texttt{%
    ...                             \\
    speak\_like\_a\_pirate(arrrgs); \\
    \only<3->{\color{myred}}explore\_sea(aye, matey);\only<3->{\color{black}}\\
    shiver(me.timbers);             \\
    ...                             \\
    }}
    \columnbreak
    \pause
    Same file from branch B:\\
    {\footnotesize\texttt{%
    ...                             \\
    speak\_like\_a\_pirate(arrrgs); \\
    \only<3->{\color{myred}}explore\_sea(me.love[0]);\only<3->{\color{black}}\\
    shiver(me.timbers);             \\
    ...
    }}
  \end{multicols}%

  \only<4->{
    Correct merge depends on the version in the merge base:\\
    {\footnotesize\texttt{%
      speak\_like\_a\_pirate(arrrgs);\\
      \only<4-5>{{\color{myblue}?????}}
      \only<6-7>{{\color{myblue}explore\_sea(aye, matey);}}
      \only<8-9>{{\color{myblue}explore\_sea(me.love[0]);}}
      \only<10-11>{{\color{myblue}explore\_sea(plus, plus);}}
      \\
      shiver(me.timbers);\\
    }}

    \only<5->{
    \vspace*\baselineskip
    \only<5>{Which we need to know to determine the merge:}
    \only<6->{Which results in the following merge:}\\
    {\footnotesize\texttt{%
      speak\_like\_a\_pirate(arrrgs);\\
      \only<6,8,10>{\qquad}
      \only<5>{{\color{mygreen}?????}}
      \only<7>{{\color{mygreen}explore\_sea(me.love[0]);}}
      \only<9>{{\color{mygreen}explore\_sea(aye, matey);}}
      \only<11>{{\color{mygreen}
      <{}<{}<{}<{}<{}<{}< HEAD  \\
      explore\_sea(aye, matey); \\
      =======\\
      explore\_sea(me.love[0]); \\
      >{}>{}>{}>{}>{}>{}> branchB
      }}
      \\
      shiver(me.timbers);\\
    }}
    }
  }

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
  \frametitle{Three-way content merge, cont.}

  git's sha1sum of individual files can be used for a shorthand:\\
    {\footnotesize\texttt{%
    \hspace*{0.6em} path\\
    1:\ sha1sum(orig:path)\\
    2:\ sha1sum(A:path)\\
    3:\ sha1sum(B:path)\\[\baselineskip]
    }}

  \pause

  For example (using shortened shas here):\\
    {\footnotesize\texttt{%
    \hspace*{0.6em} angryp.swine-latin\\
    1:\ 5ca1ab1e\\
    2:\ f005ba11\\
    3:\ b0a710ad\\[\baselineskip]
    }}

  \pause

  Where the ordering is as follows:
  {\footnotesize
  \begin{enumerate}
    \item merge base
    \item HEAD (branch checked out before running merge)
    \item other branch (the argument you passed to merge)
  \end{enumerate}
  }

  \pause

  \vspace*{0.5\baselineskip}
  git makes these accessible...

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Helpful git commands}
\begin{frame}
  \frametitle{Helpful commands}

  \only<1-8>{
  Getting details about which files are conflicted:\\
    {\footnotesize\texttt{%
    \$ git ls-files -u \\
    100644 41e3dc22a02a972d0d42 1 \qquad angryp.swine-latin\\
    100644 f185132ce93bf3e453b8 2 \qquad angryp.swine-latin\\
    100644 b506e78238513afdfbb0 3 \qquad angryp.swine-latin\\[\baselineskip]
    }}
  }

  \only<2-3>{
    Viewing other versions:\\
      {\footnotesize\texttt{%
      \$ git show :stage:filename \\
      \$ git show sha1sum \\[\baselineskip]
      }}

    \only<3>{
    Example:\\
      {\footnotesize\texttt{%
      \$ git show :2:angryp.swine-latin \\
      speak\_like\_a\_pirate(arrrgs);\\
      explore\_sea(aye, matey);\\
      shiver(me.timbers);\\[\baselineskip]
      }}
    }
  }

  \only<4-5>{
    Diffing against other versions:\\
      {\footnotesize\texttt{%
      \$ git diff [-{}-base|-{}-ours|-{}-theirs] [filename] \\
      }}

    \only<5>{
    Example:\\
      {\footnotesize\texttt{%
      \$ git diff -{}-base \\
      ...\\
      @@ -1,3 +1,7 @@\\
      \ speak\_like\_a\_pirate(arrrgs);\\
      {\color{myred}-explore\_sea(plus, plus);}\\
      {\color{mygreen}%
      +<{}<{}<{}<{}<{}<{}< HEAD\\
      +explore\_sea(aye, matey);\\
      +=======\\
      +explore\_sea(me.love[0]);\\
      +>{}>{}>{}>{}>{}>{}> branchB}\\
      \ shiver(me.timbers);\\[\baselineskip]
      }}
    }
  }

  \only<6-8>{
    Ovewriting with different versions:\\
      {\footnotesize\texttt{%
      \$ git checkout [-{}-ours|-{}-theirs] <filename> \\
      \$ git checkout [-{}-merge|-m|-{}-conflict=diff3] <filename>
          \\[0.5\baselineskip]
      }}

    \only<7>{
    Example:\\
      {\footnotesize\texttt{%
      \$ git checkout -{}-ours angryp.swine-latin \\
      \$ cat angryp.swine-latin \\
      speak\_like\_a\_pirate(arrrgs);\\
      explore\_sea(aye, matey);\\
       shiver(me.timbers);\\[\baselineskip]
      }}
    }

    \only<8>{
    Example:\\
      {\footnotesize\texttt{%
      \$ git checkout -{}-conflict=diff3 angryp.swine-latin\\
      \$ cat angryp.swine-latin \\
      speak\_like\_a\_pirate(arrrgs);\\
      <{}<{}<{}<{}<{}<{}< ours\\
      explore\_sea(aye, matey);\\
      ||||||| base\\
      explore\_sea(plus, plus);\\
      =======\\
      explore\_sea(me.love[0]);\\
      >{}>{}>{}>{}>{}>{}> theirs\\
      shiver(me.timbers);\\[\baselineskip]
      }}
    }
  }

  \only<9-12>{
    \only<9-11>{
    Can look for commits which touched conflicted files:\\[0.5\baselineskip]
      {\scriptsize\texttt{%
      \$ git log HEAD...MERGE\_HEAD -{}- \textbackslash\\
          \hspace*{10em} `git ls-files -u | awk \{print\textbackslash\$4\}`\\
      {\color{brown}commit 95d844d711a8ba9fae97 (}{\color{cyan}HEAD}, {\color{cyan}branchA}{\color{brown})}\\
      Author:\ Cap'n Blackbeard <black@beard.pirate>\\
      Date:\   Tue May 22 13:53:03 2018 -0700\\[\baselineskip]
      \qquad\!    Aye, aye\\[\baselineskip]
      {\color{brown}commit 34fa04c4a1962cf949b3 (}{\color{cyan}branchB}{\color{brown})}\\
      Author:\ Cap'n Whitebeard <white@beard.pirate>\\
      Date:\   Tue May 22 13:52:48 2018 -0700\\[\baselineskip]
      \qquad\!    Me first love\\[\baselineskip]
      }}
    }

    \only<10-11>{
      But there's an equivalent simple shorthand:\\
      {\scriptsize\texttt{%
      \$ git log -{}-merge\\[\baselineskip]
      }}
    }

    \only<11>{
      Which can be handy in combination with other flags, e.g.:\\
      {\scriptsize\texttt{%
      \$ git log -{}-merge -p -{}-oneline -{}-left-right\\
      }}
    }

    \only<12>{
      Using handy -{}-merge flag to log:\\[0.25\baselineskip]
      {\scriptsize\texttt{%
      \$ git log -{}-merge -p -{}-oneline -{}-left-right\\[0.5\baselineskip]
      {\color{blue}\textbf{<}} {\color{brown}95d844d (}{\color{cyan}HEAD}, {\color{cyan}branchA}{\color{brown})} Aye, aye\\
      diff --git a/angryp.swine-latin b/angryp.swine-latin\\
      index 41e3dc2..f185132 100644\\
      --- a/angryp.swine-latin\\
      +++ b/angryp.swine-latin\\
      @@ -1,3 +1,3 @@\\
      \ speak\_like\_a\_pirate(arrrgs);\\
      {\color{myred}-explore\_sea(plus, plus);}\\
      {\color{mygreen}+explore\_sea(aye, matey);}\\
      \ shiver(me.timbers);\\[0.5\baselineskip]
      {\color{blue}\textbf{>}} {\color{brown}34fa04c (}{\color{cyan}branchB}{\color{brown})} Me first love\\
      diff --git a/angryp.swine-latin b/angryp.swine-latin\\
      index 41e3dc2..b506e78 100644\\
      --- a/angryp.swine-latin\\
      +++ b/angryp.swine-latin\\
      @@ -1,3 +1,3 @@\\
      \ speak\_like\_a\_pirate(arrrgs);\\
      {\color{myred}-explore\_sea(plus, plus);}\\
      {\color{mygreen}+explore\_sea(me.love[0]);}\\
      \ shiver(me.timbers);\\
      }}
    }

  }

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
  \frametitle{Helpful commands}

  Pro-tip: You can ask git to check if there are conflict markers or
  whitespace errors:\\[0.25\baselineskip]
    {\scriptsize\texttt{%
    \$ git diff -{}-check\\
    angryp.swine-latin:2: leftover conflict marker\\
    angryp.swine-latin:4: leftover conflict marker\\
    angryp.swine-latin:6: leftover conflict marker\\
    }}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
  \frametitle{Helpful commands, summarized}

  Getting details about which files are conflicted:\\
    {\footnotesize\texttt{%
    \$ git ls-files -u \\[\baselineskip]
    }}

  Viewing other versions:\\
    {\footnotesize\texttt{%
    \$ git show :stage:filename \\[\baselineskip]
    }}

  Diffing against other versions:\\
    {\footnotesize\texttt{%
    \$ git diff [-{}-base|-{}-ours|-{}-theirs] [filename(s)] \\[\baselineskip]
    }}

  Ovewriting with different versions:\\
    {\footnotesize\texttt{%
    \$ git checkout [-{}-ours|-{}-theirs] <filename> \\
    \$ git checkout [-{}-merge|-m|-{}-conflict=diff3] <filename>
          \\[\baselineskip]
    }}

  Seeing which commits touched conflicted files:\\
    {\scriptsize\texttt{%
    \$ git log -{}-merge -p -{}-left-right\\[\baselineskip]
    }}

  Checking for remaining conflict markers:\\
    {\scriptsize\texttt{%
    \$ git diff -{}-check\\[\baselineskip]
    }}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Critiques/Limitations}
\begin{frame}
  \frametitle{Critiques/Limitations of three-way merge idea}

  \only<1-17>{
  Under what circumstances is using this algorithm the wrong way to merge
  three versions of the file?
  }

  \only<2-4>{
  \begin{itemize}
    \item Files must be ``normal'' (text)
    \only<3->{
    \begin{itemize}
      \item binaries
      \item symlinks
      \item submodules
    \end{itemize}
    }
  \end{itemize}
  }
  \only<4>{
    Managing: git has some smarts (and some dumbs) for merging these
    file types; look for ``binary'' in gitattributes(5).
  }

  \only<5-7>{
  \begin{itemize}
    \item Needs file ``encoding'' to be the same
    \only<6>{
    \begin{itemize}
      \item ASCII vs. EBCDIC
      \item CR vs. CRLF
      \item whitespace normalization
      \item unicode normalization
      \item other programmatic modifications -- indentation, etc.
    \end{itemize}
    }
  \end{itemize}
  }
  \only<7>{
  Managing:
  \begin{itemize}
    \item Strategy options:
    \begin{itemize}
      \item -Xrenormalize
      \item -Xignore-space-change
      \item -Xignore-all-space
      \item -Xignore-space-at-eol
      \item -Xignore-cr-at-eol
      \item -Xdiff-algorithm=[patience|minimal|histogram|myers]
    \end{itemize}
    \item Config options:
    \begin{itemize}
      \item merge.renormalize
    \end{itemize}
    \item Important manpages:
    \begin{itemize}
      \item git-merge(1) ({\tiny ``MERGE STRATEGIES'' (recursive),
                          ``CONFIGURATION''})
      \item gitattributes(5)
    \end{itemize}
  \end{itemize}
  }

  \only<8-10>{
  \begin{itemize}
    \item Assumes conflict markers are distinguishable from other text
    \only<9->{
    \begin{itemize}
      \item What if you're writing documentation about how conflicts work?
    \end{itemize}
    }
  \end{itemize}
  }
  \only<10>{
  Managing: See ``conflict-marker-size'' in gitattributes(5)
  }

  \only<11-13>{
  \begin{itemize}
    \item Assumes line-based (vs. word-based) diffing
    \only<12->{
    \begin{itemize}
      \item books
      \item documentation
      \item articles
    \end{itemize}
    }
  \end{itemize}
  }
  \only<13>{
    Managing: Um...don't re-wrap or just suck up extra conflicts?
  }

  \only<14-17>{
  \begin{itemize}
    \item Text-based diff ignores (most) semantic content
    \only<15->{
    \begin{itemize}
      \item both branches add a new import on the same line
      \item one branch adds call to a function, another adds an argument to it
    \end{itemize}
    }
  \end{itemize}
  }
  \only<16-17>{
  \begin{multicols}{2}
    File from branch A:\\
    {\footnotesize\texttt{%
    ...                             \\
    {\color{myred}-def inspect\_ship(cannons, mast)} \\
    {\color{mygreen}+def inspect\_ship(cannons, mast, plank)} \\
    ...                             \\
    }}
    \columnbreak
    \pause
    Different file from branch B:\\
    {\footnotesize\texttt{%
    ...                             \\
    {\color{mygreen}+inspect\_ship(MHWCK\_045026, big\_pole)} \\
    ...
    }}
  \end{multicols}%
  }
  \only<17>{
    Managing: For some cases, extra manual conflict resolution.  For
    other cases, make sure to build and test the merged result, not
    just the proposed change.
  }

  \only<18-19>{
    Big hammer: See ``custom merge driver'' in gitattributes(5)
    \only<19>{
    \begin{itemize}
      \item Can define \texttt{merge.<driver>.\{name,driver\}}
      \item Local-only, though
    \end{itemize}
    }
  }

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
  \frametitle{Critiques/Limitations of three-way merge idea}

  Under what circumstances is using this algorithm the wrong way to merge
  three versions of the file?

  \only<2->{
  \begin{itemize}
    \item Ignores intermediate history
    \only<3->{
    \begin{itemize}
      \item Same fix applied on both branches.  Later, additional fixes were
            made to the same lines on one branch.

      \only<4->{
      \item A ``fix'' was applied on both branches (cherry-picked or
            manually committed in both places), but then reverted on one
            side because it's harmful.
      }

    \end{itemize}
    }
  \end{itemize}
  }

  \only<5>{

    Managing: For some cases, extra manual conflict resolution.  For
    other cases, make sure to build and test the merged result, not
    just the proposed change.

    \vspace*{\baselineskip}
    (If these two cases bother you enough, consider darcs or
    \href{https://jneem.github.io/merging/}{\color{myblue}pijul}.)  }

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Applicability of three-way content merges}
\begin{frame}
  \frametitle{Applicability of three-way content merges}

  Under what circumstances is using this algorithm the wrong way to
  merge \only<1>{three versions}\only<2->{\textbf{\textit{three
  versions}}} of \only<1-2>{the}\only<3->{\textbf{\textit{the}}}
  file?

  \only<4->{
  \begin{itemize}
    \item Can we assume that the same pathname at different points of history
      implies the content is related?  (e.g. could delete a file and add an
      unrelated one back.)
    \only<5->{
    \item Can we assume that the only related content for a file will be
      found at the same pathname?
    \only<6->{
    \item Can we assume there are three versions of each ``file''?
    }}
  \end{itemize}
  }

  \only<7->{
  Let's dig in, except:
  \begin{itemize}
    \item Git does not (yet?) do break detection (determining whether
          same-named files are no longer related) for merges.
    \only<8->{
    \item Git does not (yet?) check for movement of blocks of code between
          files (e.g. a function moved to a different file in one branch,
          and that function was modified on other branch) for merges.  It does
          detect code movement as part of git blame, assuming appropriate flags
          are passed.
    }
  \end{itemize}
  }

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
  \frametitle{Applicability of three-way content merges}

  Assuming previous page problems aren't an issue {\scriptsize (i.e.\
  \begin{itemize}
    \item Normal files
    \item Same ``encoding''
    \item No conflict markers already present
    \item Line-based is okay
    \item Files with same name are related
    \item Content doesn't move between filenames
    \item We have three versions of every file in each revsion
  \end{itemize}
  } what kinds of errors might Git report as preventing a
  successful merge?

  \only<2->{
  \begin{itemize}
    \item Content conflicts
    \only<3->{
    \item User has changes staged but not yet committed
    \only<4->{
    \item User has unstaged changes that would be overwritten
      \only<5->{
        \begin{itemize}
        \item Unstaged delete could come with untracked directory in the way
          \end{itemize}
    }}}
  \end{itemize}
  }

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
  \frametitle{Applicability of three-way content merges}

  Assuming we can delete files, what additional kinds of conflicts can we get?
  \pause
  \begin{itemize}
    \item modify/delete
    \pause
    \item untracked file in the way of content
    \pause
    \item untracked directory in the way
  \end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
  \frametitle{Applicability of three-way content merges}

  Assuming we can also add files, what additional kinds of conflicts can we get?
  \pause
  \begin{itemize}
    \item add/add (both sides add foo)
    \pause
    \item directory/file (add foo vs. add foo/bar)
    \pause
    \item submodule/file
    \pause
    \item submodule/directory
  \end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
  \frametitle{Applicability of three-way content merges}

  Assuming we can also rename files, what additional kinds of
  conflicts can we get?
  \pause
  \begin{itemize}
    \item rename/del
          {\scriptsize (A $\Rightarrow$ B vs. delete A)}
    \pause
    \item rename/add
          {\scriptsize (A $\Rightarrow$ B vs. add B)}
    \pause
    \item rename/add/del
          {\scriptsize (A $\Rightarrow$ B vs. delete A \& add different B)}
    \pause
    \item rename/rename(1to2)
          {\scriptsize (A $\Rightarrow$ B vs. A $\Rightarrow$ C)}
    \pause
    \item rename/rename(1to2)/add/add
          {\scriptsize (A $\Rightarrow$ B, add C vs. A $\Rightarrow$ C, add B)}
    \pause
    \item rename/rename(2to1)
          {\scriptsize (B $\Rightarrow$ A vs. C $\Rightarrow$ A)}
    \pause
    \item rename/rename(2to1)/del/del
          {\scriptsize (B $\Rightarrow$ A, delete C vs.
                        C $\Rightarrow$ A, delete B)}
    \pause
    \item chains of rename/rename(1to2) and rename/rename(2to1)
          {\scriptsize (A $\Rightarrow$ B, C $\Rightarrow$ D, E $\Rightarrow$ F
                        vs.
                        A $\Rightarrow$ F, C $\Rightarrow$ B, E $\Rightarrow$ D)}

  \end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
  \frametitle{Applicability of three-way content merges}

  What if there is no merge base?
  \pause
  \\[\baselineskip]
  Turns any pair of non-identical files into add/add conflicts.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
  \frametitle{Applicability of three-way content merges}

  What if there are multiple merges bases?
  \pause
  \\[\baselineskip]
  Merge the merge bases!
  \pause
  \\[\baselineskip]
  ...but do NOT error out with conflicts.  Instead, forcibly resolve:
  \pause
  \begin{itemize}[<+->]
    \item content conflicts
    \item modify/delete
    \item special files: binary, symlink, submodule
    \item directory/file, directory/submodule, submodule/file
    \item rename/delete
    \item rename/add
    \item rename/add/delete
    \item rename/rename(1to2)
    \item rename/rename(1to2)/add/add
    \item rename/rename(2to1)
    \item rename/rename(2to1)/delete/delete
    \item chains of rename/rename(1to2) and rename/rename(2to1)
    \item mode conflict (file/symlink, submodule/file, exec./plain, etc.)
  \end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
  \frametitle{Applicability of three-way content merges}

  Some things you may have not noticed:
  \begin{itemize}[<+->]
    \item May not readily be able to represent conflicts by adding content
          to a file at the specified path(s).
    \item Desired content may not be writable at specified file location
    \item More than three versions of a file possible (4 or 6)
    \item Each conflict type has three different resolutions
    \begin{itemize}
      \item working tree
      \item index
      \item recursive-merge-base
    \end{itemize}
    \item Nested conflict markers
    \item Avoiding unnecessary updates
    \item Dirty changes and untracked files have many ways of getting
          in the way, especially with current design
    \item Implementation issues that bubble up to the user
    \begin{itemize}
      \item rename detection heuristics
      \item diff algorithm (see -Xdiff-algorithm)
      \item writing intermediate file-merges to object store immediately
    \end{itemize}
  \end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Caveats}
\begin{frame}
  \frametitle{Caveats}

  {\scriptsize

  Critiques/Limitations of three-way merge idea\\[-0.5\baselineskip]
  \begin{myitemize}
    \item File Content
      \begin{myitemize}\scriptsize
        \item Files must be ``normal'' (text)%; counter-examples:
          %* binary
          %* symlinks
          %* submodules
        \item Needs file ``encoding'' to be the same% (merge.renormalize); issues:
          %* ASCII vs. EBCDIC (yeah, sure)
          %* CR vs. CRLF (happens...)
          %* whitespace normalization?
          %* unicode normalization?
          %* other programmatic modifications -- indentation, etc.?
        \item Assumes conflict markers are distinguishable from other text
          % What if you're writing documenting, about how git-merge works?
        \item Assumes line-based diffing%; issues:
          %* journal, documentation, word-based articles
        \item Text-based diff ignores semantic content%; issues:
          %* one branch adds call to a function, another adds an argument to it
      \end{myitemize}\vspace*{-0.3\baselineskip}
    \item Ignores intermediate history%; issues:
      %* "fix" applied on both sides, then reverted on one side because it's
      %  harmful...
      %* same fix on both sides, extra fixes on other side in same region =>
      %  conflicts
      %* however, three-way merge is hard enough for people to understand.
      %  Explaining a conflict that arises from intermediate history might
      %  become truly baffling
  \end{myitemize}\vspace*{-0.3\baselineskip}

  Applicability of three-way content merges:\\[-0.7\baselineskip]
  \begin{myitemize}
    \item Merge-base
      \begin{myitemize}\scriptsize
      \item exists%; counter-examples:
        %* merging independent repositories -- do two-way merge
      \item unique%; counter-examples:
        %* lots; see git.git and linux.git.  unlikely with central server and
        %  merge-to-mainline workflow
        %* follow-on assumption: merge-base can be constructed by just merging
        %  the others together (counter-examples: conflicts, including crazy types)
        %* follow-on assumption: we can find something meaningful to use as a
        %  merge-base and construct it as a tree (maybe...)
      \end{myitemize}\vspace*{-0.3\baselineskip}
    \item File versions
      \begin{myitemize}\scriptsize
        \item Three versions of each file exist%; counter-examples:
          %* one version
          % * existed in base \& deleted on both sides
          % * new file unique to one side (possible D/F conflict...)
          %* two versions
          %  * didn't exist in base; add/add conflict unless identical
          %  * did exist in base: modify/delete unless unmodified
          %* more than three versions: (see combination effects)
        \item The three versions of the file have same pathname
          %* whoo, boy, this is a big can of worms
        \item If there are three versions of pathname, they're related%; counter-examples:
          %* simple rename/modify (use O,A,B notation to show modify/delete+add)
          %* one renamed away, with new file in place
          %* one file deleted, new file now in its place
          %* swap rename (a->b, b->a)
          %* (This could get really complicated, but git doesn't do break detection
          %   for merges, so not relevant right now)
          \end{myitemize}\vspace*{-0.3\baselineskip}
    \item Chunks of lines (e.g. functions) do not move between files
      %* git handles this in blame, but not for merges.  At least not yet.
  \end{myitemize}\vspace*{-0.3\baselineskip}

  Subtle assumptions:\\[-0.5\baselineskip]
  \begin{myitemize}
    \item Path for a file is writable %(whoops)
    \item No nesting of conflict markers %(ha!)
    \item Conflicts representable on disk
      %(oops: modify/delete, D/F, submodule/file,
      %submodule/directory, submodule/submodule, rename/rename(1to2), directory
      %rename detection issues)
  \end{myitemize}\vspace*{-0.3\baselineskip}

  Implementation limits:\\[-0.5\baselineskip]
  \begin{myitemize}
    \item Dirty changes
    \item Rename heuristics
    \item Writing intermediate file-merges to object store immediately
  \end{myitemize}

  }

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Directory rename detection}
\begin{frame}
  \frametitle{Directory rename detection}

  More fun:
  \begin{itemize}[<+->]
    \item Splitting a directory into two (or more)
    \item ``Partial'' directory rename

    \item Transitive renaming
    \item rename/rename(2to1), but only due to transitive rename
    \item Multiply transitive renames

    \item Don't apply other side's rename if we did the same rename

    \item Files/directories in the way of subset of to-be-renamed paths

    \item Instead of rename, merge a directory with another
    \item N-to-1 directory merge

    \item Nested directory also renamed (and outside of parent)
    \item Dual directory rename, one into the other's way
    \item Renaming directory and basenames of each file within it
    \item Renamed directory contained subdirs (possibly also renamed), not files

  \end{itemize}

\end{frame}

\end{document}
